### 2015-11-11 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
viele viele bunte smarties

Assume two sequences of length t with l mismatches. In the worst case, all mismatches are 
distributed uniformly. Than both sequences will share $l+1$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$.\\
\\
\noindent So both sequences share $l+1$ k-tuples of length $k = \lfloor\frac{t}{l+1}\rfloor$ and for each 
$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $l+1 * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
k-tuples.

@@

>>>>

Assume two sequences of length t with l mismatches. In the worst case, all mismatches are 
distributed uniformly. Than both sequences will share $l+1$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$.\\
\\
\noindent So both sequences share $l+1$ k-tuples of length $k = \lfloor\frac{t}{l+1}\rfloor$ and for each 
$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
k-tuples.

@@

The feasible region of this linear program is shown in figure \ref{feasibleRegion}, where the red line 
is constraint 1, green line is constraint 2, constraint 3 is drawn as a blue line and the yellow line 
is constraint 4.

\begin{figure}[ht]
 \centering
 \includegraphics[width=0.7\textwidth]{img/figure_1.png}
 \caption{feasible region of linear program}
 \label{feasibleRegion}
\end{figure}
